Notebook with AMP-AD RNA-seq network analysis results

### 2020-01-03 manuscript.Rmd
remove utility function dependencies

Build aggregate modules from individual modules and differential expression meta-analysis, this will give you the same modules as are stored at synXXXver.x

>>>>

Build aggregate modules from individual modules and differential expression meta-analysis, this will give you the same modules as are stored at syn11932957
